\documentclass[12pt]{article}
\usepackage[a4paper, left=1in,right=1in,top=1in,bottom=1in]{geometry}
\usepackage{setspace} \begin{document}

\centerline{Coop Reflection}

My coop this semester was at Applause. Applause creates testing software for
various web and mobile apps. They provide "in the wild" testing, which is a
community of testers managed by software we created and project managers we
assigned. They delegate testing to groups in the community.

I was placed in charge of creating a status page that would display the status
of all of our products we offered. It would show if they were up and running
smoothly or if they were down or if they were running with degraded performance.

In order to accomplish this, I needed to create a Node.js application that would
communicate with two different API's. Before this project, I had no experience
working with any form of Javascript. I ran through several tutorials and decided
to dive in head first. I learned about asynchronous calls and my mentor there
guided me through any confusions I had. He was especially helpful when
explaining promises.

Promises were the trickiest part of Javascript. I read through several articles
online, but I realized none of the information was making sense. I then when to
my mentor and he was able to point me in the right direction and explained how
they were useful in my specific scenario. I then decided to create simple
examples of promises in order to figure out how they worked. I eventually got
it. I realize now, that reading tutorials online will often only get you a
general understanding of a concept. You will not fully understand the details of
a concept until you actually create examples for yourself.

This coop was almost entirely in line with my goals and intentions. I wanted a
small development environment using a modern and widely used language. Working
at Applause easilty satisfied that criteria.

After working at Applause, I now have another language under my belt that I can
say I have worked in. Concurrently, I have also created a side project using the
skills I developed here which I can definitely put down on my resume.

\end{document}
